Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-10-29 prob.tex
prob.tex \section{Proof} Delete duplicated definition...
prob.tex \section{Proof} Add citation...

\begin{definition}For any continuous function~$f:S^{d-1}\rightarrow\mathbb{R}$,
the modulus of continuity of $f$ is given by $\omega_{f}\left(\delta\right)=\sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|$.\qed\end{definition}

\begin{definition}For any continuous function~$f:S^{d-1}\rightarrow\mathbb{R}$,
the modulus of continuity of $f$ is given by $\omega_{f}\left(\delta\right)=\sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|$.\qed\end{definition}

>>>>

\begin{definition}\cite{WheedenZygmund1977}~For any continuous
function~$f:S^{d-1}\rightarrow\mathbb{R}$, the modulus of continuity
of $f$ is given by $\omega_{f}\left(\delta\right)=\sup_{\left\Vert \ket{\psi}-\ket{\phi}\right\Vert <\delta}\left|f\left(\ket{\psi}\right)-f\left(\ket{\phi}\right)\right|$.\qed\end{definition}
